\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
06.30 - 07.00 & Yu. B.  Ivanov\\ 
25+5 min. & {\it Three-fluid Hydrodynamics-based Event Simulator Extended by UrQMD final State interactions  (THESEUS) for FAIR-NICA-SPS-BES/RHIC energies}\\ 
 & \\ 
07.00 - 07.30 & Hanna Zbroszczyk\\ 
25+5 min. & {\it Two-particle correlations using THERMINATOR model for BES program}\\ 
 & \\ 
08.00 - 08.30 & Kyrill Bugaev\\ 
25+5 min. & {\it Probing the tricritical endpoint of QCD phase diagram at NICA-FAIR energies}\\ 
 & \\ 
08.30 - 09.00 & Oleksii Ivanytskyi\\ 
25+5 min. & {\it Separate freeze-out of strange particles and the quark-hadron phase transition}\\ 
 & \\ 
09.30 - 10.00 & Antoni Marcinek\\ 
25+5 min. & {\it New Baryonic and Mesonic Observables from NA61/SHINE}\\ 
 & \\ 
12.00 - 12.30 & Andrej Kugler\\ 
25+5 min. & {\it Flow at SIS energies - overview of SIS18 results and prospect for SIS100}\\ 
 & \\ 
12.30 - 13.00 & Chi Yang\\ 
25+5 min. & {\it The STAR detector upgrade and future plan}\\ 
 & \\ 
05.30 - 06.00 & Mikhail Kapishin\\ 
25+5 min. & {\it BM@N experiment for studies of Baryonic Matter at the Nuclotron}\\ 
 & \\ 
06.00 - 06.30 & Volker Friese\\ 
25+5 min. & {\it Physics with the CBM experiment}\\ 
 & \\ 
06.30 - 07.00 & Ivan Kisel\\ 
25+5 min. & {\it Event topology reconstruction in the CBM experiment at FAIR}\\ 
 & \\ 
07.00 - 07.30 & You Zhou\\ 
25+5 min. & {\it Correlations of anisotropic flow in relativistic heavy-ion collisions at the LHC}\\ 
 & \\ 
08.00 - 08.30 & Vladimir Kekelidze\\ 
25+5 min. & {\it Multi Purpose Detector at NICA: Status and Prospects}\\ 
 & \\ 
08.30 - 09.00 & Grigory Nigmatkulov\\ 
25+5 min. & {\it Pion and kaon Bose-Einstein correlations from the BES program at STAR}\\ 
 & \\ 
\end{longtable}

