\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
08.00 - 08.30 & Dirk Rischke\\ 
25+5 min. & {\it Anisotropic dissipative fluid dynamics}\\ 
 & \\ 
08.30 - 09.00 & Carsten Greiner\\ 
25+5 min. & {\it Comparison of hydrodynamical and transport theoretical calculations for p+A and A+A collisions}\\ 
 & \\ 
09.00 - 09.30 & Gottfried Münzenberg\\ 
25+5 min. & {\it Super Heavy Elements -  experimental developments}\\ 
 & \\ 
09.30 - 10.00 & Igor Mishustin\\ 
25+5 min. & {\it Greiner and exotic matter}\\ 
 & \\ 
10.00 - 10.30 & Mikhail Itkis\\ 
25+5 min. & {\it Experimental investigation of fusion-fission mechanisms for superheavy nuclei}\\ 
 & \\ 
08.50 - 09.20 & Sigurd Hofmann\\ 
25+5 min. & {\it Eighty Years of Research on Super-heavy Elements}\\ 
 & \\ 
09.20 - 09.50 & Stefan Schramm\\ 
25+5 min. & {\it TBA}\\ 
 & \\ 
09.50 - 10.20 & Alexander Sorin\\ 
25+5 min. & {\it Vorticity and polarization in baryon-rich matter formed in heavy ion collisions}\\ 
 & \\ 
12.00 - 12.30 & Larissa Bravina\\ 
25+5 min. & {\it TBA}\\ 
 & \\ 
12.30 - 13.00 & Alexandre Gumberidze\\ 
25+5 min. & {\it Atomic physics with highly-charged heavy ions at GSI/FAIR}\\ 
 & \\ 
13.30 - 14.00 & Dorin  Poenaru\\ 
25+5 min. & {\it Alpha and cluster decay of few super heavy nuclei. Under barrier fusion to produce Super heavy Nuclei.}\\ 
 & \\ 
14.00 - 14.30 & CHHANDA SAMANTA\\ 
25+5 min. & {\it Superheavy Nuclei to Hypernuclei: A Tribute to Walter Greiner}\\ 
 & \\ 
14.30 - 15.00 & Nabanita Dasgupta-Schubert\\ 
25+5 min. & {\it Predictability analysis of α decay formulae and the α partial half-lives of exotic nuclei.}\\ 
 & \\ 
\end{longtable}

