\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
08.00 - 08.30 & Maria Chekhova\\ 
25+5 min. & {\it Phase supersensitivity in an unbalanced SU(1,1) interferometer}\\ 
 & \\ 
08.30 - 09.00 & U L Andersen\\ 
25+5 min. & {\it Squeezed light enhanced sensing of a micro-mechanical oscillator}\\ 
 & \\ 
09.00 - 09.30 & Radim Filip\\ 
25+5 min. & {\it Highly nonlinear quantum optics and optomechanics}\\ 
 & \\ 
09.30 - 10.00 & Christian Ralf Müller\\ 
25+5 min. & {\it From Quantum-Limited Measurements towards Quantum Squeezing Detection over Satellite Links}\\ 
 & \\ 
12.00 - 12.20 & Vladimir Shevchenko\\ 
15+5 min. & {\it Quantum measurements in finite space-time domain}\\ 
 & \\ 
12.20 - 12.40 & Aurelian Isar\\ 
15+5 min. & {\it Dynamics of quantum correlations in two-mode Gaussian open quantum systems}\\ 
 & \\ 
12.40 - 13.00 & Mihaescu Tatiana\\ 
15+5 min. & {\it Gaussian quantum steering of two bosonic modes in a squeezed thermal environment}\\ 
 & \\ 
13.30 - 14.00 & Ladislav Mista\\ 
25+5 min. & {\it Gaussian intrinsic entanglement}\\ 
 & \\ 
14.00 - 14.30 & Petros Wallden\\ 
25+5 min. & {\it Relativistic and Device Independent Verifiable Quantum Computation}\\ 
 & \\ 
14.30 - 14.50 & Matthew Thornton\\ 
15+5 min. & {\it Gigahertz quantum signatures compatible with telecommunication technologies}\\ 
 & \\ 
14.50 - 15.10 & Tom Douce\\ 
15+5 min. & {\it Quantum advantage and fault tolerant universal quantum computing in continuous variables}\\ 
 & \\ 
08.00 - 08.30 & Claude Fabre\\ 
25+5 min. & {\it Quantum Frequency Combs: generation, characterization and applications}\\ 
 & \\ 
08.30 - 09.00 & Nicolas Menicucci\\ 
25+5 min. & {\it Continuous quantum variables: from quantum computing to relativistic quantum information}\\ 
 & \\ 
09.00 - 09.30 & David Edward Bruschi\\ 
25+5 min. & {\it Work is the source of gravity}\\ 
 & \\ 
09.30 - 10.00 & Sorin Paraoanu\\ 
25+5 min. & {\it Tripartite continuous-variables coherence and entanglement from vacuum fluctuations}\\ 
 & \\ 
12.20 - 12.40 & Avi Pe'er\\ 
15+5 min. & {\it Ultrafast Quantum Key Distribution with Ultra-Broad Squeezed Light}\\ 
 & \\ 
12.40 - 13.00 & Théo Torres Vicente\\ 
15+5 min. & {\it Observing superradiance in a vortex flow}\\ 
 & \\ 
13.30 - 14.00 & Andrzej Dragan\\ 
25+5 min. & {\it Counting Unruh particles}\\ 
 & \\ 
14.00 - 14.20 & Maxime Jacquet\\ 
15+5 min. & {\it Mixing of positive and negative frequency waves at the optical horizon}\\ 
 & \\ 
14.20 - 14.40 & Woods Mischa\\ 
15+5 min. & {\it Autonomous quantum machines and finite sized clocks}\\ 
 & \\ 
14.40 - 15.10 & Vesna Berec\\ 
25+5 min. & {\it Quantum networks: topology and spectral characterization}\\ 
 & \\ 
\end{longtable}

