\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
16.30 - 17.30 & Frederic Lassiaille\\ 
55+5 min. & {\it Surrounding matter theory}\\ 
 & \\ 
16.30 - 17.30 & HEXI SHI\\ 
55+5 min. & {\it Search for the violation of Pauli principle at LNGS - first physics result of VIP2 experiment}\\ 
 & \\ 
16.30 - 17.00 & Andre Sopczak\\ 
25+5 min. & {\it ttH Coupling Measurement with the ATLAS Detector at the LHC}\\ 
 & \\ 
16.30 - 17.30 & Wim De Boer\\ 
55+5 min. & {\it Molecular Clouds as the Origin of the Gamma-Ray GeV excess}\\ 
 & \\ 
16.30 - 17.30 & marjan abbasipour\\ 
55+5 min. & {\it Modification of Material Surface by Plasma}\\ 
 & \\ 
16.30 - 17.30 & Igor Bulyzhenkov\\ 
55+5 min. & {\it Gravity until equipartition of relativistic kinetic energies.}\\ 
 & \\ 
16.30 - 17.30 & Timur Kamalov\\ 
55+5 min. & {\it Quantum Correction for Newton’s Law of Motion}\\ 
 & \\ 
16.30 - 17.30 & CHHANDA SAMANTA\\ 
55+5 min. & {\it A-dependence of $\Lambda\Lambda$-bond and charge symmetry energies}\\ 
 & \\ 
16.30 - 17.30 & shihan sajeed\\ 
55+5 min. & {\it Insecurity of detector-device-independent quantum key distribution}\\ 
 & \\ 
16.30 - 17.30 & Luigi Marchese, Luigi Marchese\\ 
55+5 min. & {\it muon performance}\\ 
 & \\ 
16.30 - 17.30 & Alessandro Romito\\ 
55+5 min. & {\it Thermodynamics along individual trajectories of a quantum bit}\\ 
 & \\ 
16.30 - 17.30 & Jorge Bernal Arroyo\\ 
55+5 min. & {\it New Mathematical Formulation of the Correspondence Principle}\\ 
 & \\ 
16.30 - 17.30 & Gopinath Kamath\\ 
55+5 min. & {\it Cylindrical symmetry: II. The Green’s function in 3 + 1 dimensional curved space}\\ 
 & \\ 
16.30 - 17.30 & Luis Gonzalez-Mestres\\ 
55+5 min. & {\it New particles and nonstandard new Physics}\\ 
 & \\ 
16.30 - 17.30 & Valerio Mascagna\\ 
55+5 min. & {\it Experimental technique for $\mathrm{\bar{p}}$-nucleus annihilation cross section measurements at low energy}\\ 
 & \\ 
16.30 - 17.30 & Luca Venturelli\\ 
55+5 min. & {\it Antiproton-nucleus annihilation cross section at low energy}\\ 
 & \\ 
16.30 - 17.30 & Christian Farnese\\ 
55+5 min. & {\it The new front end and DAQ of the ICARUS detector}\\ 
 & \\ 
16.30 - 17.30 & Ryan Parker\\ 
55+5 min. & {\it Hybrid Photonic Loss Resilient Entanglement Swapping}\\ 
 & \\ 
16.30 - 17.30 & Virendrasinh H. Kher, Nayneshkumar Devlani, Ajay Kumar Rai\\ 
55+5 min. & {\it Radiative transitions and the mixing parameters of the D meson}\\ 
 & \\ 
16.30 - 17.30 & Zalak Marfatia, Ajay Kumar Rai\\ 
55+5 min. & {\it Heavy baryon spectroscopy in Hypercentral constituent quark model}\\ 
 & \\ 
16.30 - 17.30 & Adam Balcerzak\\ 
55+5 min. & {\it Varying constants quantum cosmologies}\\ 
 & \\ 
16.30 - 17.30 & Yifan Cheng\\ 
55+5 min. & {\it Possible Approach to Dynamical Supersymmetry Breaking via Nambu--Jona-Lasinio Model}\\ 
 & \\ 
16.30 - 17.30 & Georgios Karathanasis\\ 
55+5 min. & {\it The new CMS Barrel Muon Track Finder}\\ 
 & \\ 
16.30 - 17.30 & Alexander Joan Cristo Juárez-Domínguez\\ 
55+5 min. & {\it Quantization Aspects of a Hypercomplex Field}\\ 
 & \\ 
16.30 - 17.30 & Swagata Mukherjee\\ 
55+5 min. & {\it Search for R-parity violating supersymmetry and Quantum black-holes in e+mu final state in CMS}\\ 
 & \\ 
16.30 - 17.30 & Ömer Bayraktar\\ 
55+5 min. & {\it Experimental Relativistic Quantum Information with a Geostationary Satellite}\\ 
 & \\ 
16.30 - 17.30 & Andrea Lavagno\\ 
55+5 min. & {\it Nuclear phase transition and thermodynamic instabilities in dense nuclear matter}\\ 
 & \\ 
16.30 - 17.30 & Mohammad M. Qaemmaqami\\ 
55+5 min. & {\it On the Butterfly Effect in 3D Gravity}\\ 
 & \\ 
16.30 - 17.30 & Anna Stakia\\ 
55+5 min. & {\it Search for supersymmetry in events with one lepton, multiple jets and missing transverse momentum in proton-proton collisions at √s = 13 TeV}\\ 
 & \\ 
16.30 - 17.30 & Anna Stakia\\ 
55+5 min. & {\it Jet-flavour tagging using deep-learning in the CMS experiment}\\ 
 & \\ 
16.30 - 17.30 & Ralf Seidl\\ 
55+5 min. & {\it Latest results on azimuthal anisotropy at RHIC-PHENIX}\\ 
 & \\ 
17.00 - 17.30 & Elisaveta Zherebtsova\\ 
25+5 min. & {\it Procedure for event characterization in Pb-Pb collisions at 40AGeV in the NA49 experiment at CERN SPS}\\ 
 & \\ 
17.10 - 17.30 & Laszlo Csernai\\ 
15+5 min. & {\it Applications of Advances in Relativistic Fluid Dynamics to Laser Fusion}\\ 
 & \\ 
17.10 - 17.30 & Cristiano Sebastiani\\ 
15+5 min. & {\it Search for displaced lepton jets with the ATLAS experiment}\\ 
 & \\ 
17.10 - 17.30 & Oleksii Ivanytskyi\\ 
15+5 min. & {\it On bimodal size distribution of spin clusters in the one-dimensional Ising model}\\ 
 & \\ 
\end{longtable}

