\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
12.00 - 12.30 & Violetta Sagun\\ 
25+5 min. & {\it Neutron stars equation of state consistent with high-energy nuclear physics data}\\ 
 & \\ 
13.30 - 14.00 & Alexandros Gezerlis\\ 
25+5 min. & {\it Strongly interacting matter in neutron stars}\\ 
 & \\ 
08.00 - 08.30 & Roman Kolevatov\\ 
25+5 min. & {\it Cosmological bounce and Genesis beyond Horndeski}\\ 
 & \\ 
08.30 - 09.00 & Victoria Volkova\\ 
25+5 min. & {\it On perturbations in Horndeski theories}\\ 
 & \\ 
09.00 - 09.30 & Paul Saffin\\ 
25+5 min. & {\it Fermions from Oscillons}\\ 
 & \\ 
09.30 - 10.00 & Igor Mishustin\\ 
25+5 min. & {\it Self-consistent calculations of supernova matter}\\ 
 & \\ 
10.00 - 10.30 & Ryuji Takeishi\\ 
25+5 min. & {\it Observation of ultra-high energy cosmic rays with the Telescope Array experiment}\\ 
 & \\ 
12.00 - 12.30 & Kostas Glampedakis\\ 
25+5 min. & {\it Observationally constraining gravitational wave emission from short gamma-ray burst remnants}\\ 
 & \\ 
12.30 - 13.00 & Georgy Burde\\ 
25+5 min. & {\it Relativity with a preferred frame. Astrophysical and cosmological implications}\\ 
 & \\ 
13.30 - 14.00 & Fabio Cappella\\ 
25+5 min. & {\it Search for rare processes with DAMA experimental set-ups}\\ 
 & \\ 
08.00 - 08.30 & Vincenzo Caracciolo\\ 
25+5 min. & {\it DAMA/LIBRA results and perspectives}\\ 
 & \\ 
08.30 - 09.00 & Petr Blaschke\\ 
25+5 min. & {\it Pedal coordinate, dark Kepler and other force problems}\\ 
 & \\ 
09.00 - 09.30 & Martin Stahlberg\\ 
25+5 min. & {\it Direct dark matter search with ultra-low thresholds in the CRESST-III experiment}\\ 
 & \\ 
12.00 - 12.30 & Keiko Nagao\\ 
25+5 min. & {\it Anisotropy of dark matter velocity distribution measured with directional detection}\\ 
 & \\ 
08.00 - 08.30 & Anton Chudaykin\\ 
25+5 min. & {\it Heavy sterile neutrino with large mixing angle does not contradict cosmology}\\ 
 & \\ 
09.00 - 09.30 & Alexander Borisov\\ 
25+5 min. & {\it Exotic events in cosmic ray experiments at super high energies: a manifestation of New Physics?}\\ 
 & \\ 
12.00 - 12.30 & https://me.yahoo.com/a/NjbRTy15qdwcUkUX\_tupKsRRNjAALA--\#0d66d Zlatanovic\\ 
25+5 min. & {\it Geodesic mapping for non-symmetric gravitation theory (NGT) with torsion}\\ 
 & \\ 
13.30 - 14.00 & Maxim Fitkevich\\ 
25+5 min. & {\it Dilaton gravity with a boundary: current progress}\\ 
 & \\ 
14.00 - 14.30 & Predrag Dominis Prester\\ 
25+5 min. & {\it Pontryagin trace anomaly}\\ 
 & \\ 
05.30 - 06.00 & Luis Gonzalez-Mestres\\ 
25+5 min. & {\it The physical vacuum in standard theories and in alternative approaches}\\ 
 & \\ 
06.00 - 06.30 & Sergey Godunov\\ 
25+5 min. & {\it Domain Walls in the Early Universe and Generation of Matter and Antimatter Domains}\\ 
 & \\ 
06.30 - 07.00 & Hovik Grigorian\\ 
25+5 min. & {\it Cooling of Compact High Mass Twin Stars}\\ 
 & \\ 
08.00 - 08.30 & Constantinos Constantinou\\ 
25+5 min. & {\it Hot and dense nuclear matter in astrophysics}\\ 
 & \\ 
\end{longtable}

