\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
06.00 - 06.30 & Wim De Boer\\ 
25+5 min. & {\it Perspectives on Detection of  supersymmetric Dark Matter}\\ 
 & \\ 
06.30 - 07.00 & Yongmin CHO\\ 
25+5 min. & {\it Cosmic Electroweak Monopole}\\ 
 & \\ 
07.00 - 07.30 & John Ellis\\ 
25+5 min. & {\it LHC Constraint on Light-by-light Scattering, Born-Infeld theory and the mass of an Electroweak Monopole}\\ 
 & \\ 
08.00 - 08.30 & sarben sarkar\\ 
25+5 min. & {\it Magnetic Monopoles from Global Monopoles in the presence of a Kalb-Ramond Field}\\ 
 & \\ 
08.30 - 09.00 & Laura Patrizii\\ 
25+5 min. & {\it Status of the searches for Magnetic Monopoles}\\ 
 & \\ 
09.00 - 09.30 & Frederik Lauber\\ 
25+5 min. & {\it Magnetic monopole searches with IceCube}\\ 
 & \\ 
09.30 - 10.00 & Adrian Bevan\\ 
25+5 min. & {\it Searching for monopoles in polar ice samples}\\ 
 & \\ 
12.00 - 12.30 & James Pinfold\\ 
25+5 min. & {\it The MoEDAL Experiment Past, Present and Future.}\\ 
 & \\ 
12.30 - 13.00 & Richard Soluk\\ 
25+5 min. & {\it The MoEDAL Detector at the LHC}\\ 
 & \\ 
14.00 - 14.30 & Igor Ostrovskiy\\ 
25+5 min. & {\it Searching for magnetic monopoles with Solid State Breakdown Counters: from LHC to Space}\\ 
 & \\ 
14.30 - 15.00 & Oliver Gould\\ 
25+5 min. & {\it Magnetic monopole production in heavy ion collisions}\\ 
 & \\ 
15.10 - 15.40 & Jonathan Hays\\ 
25+5 min. & {\it Machine LEarning, Monopoles and MoEDAL}\\ 
 & \\ 
15.40 - 16.10 & Daniela Bauer\\ 
25+5 min. & {\it Distributed Computing for Small Collaborations}\\ 
 & \\ 
16.10 - 16.30 & Arka Santra\\ 
15+5 min. & {\it Magnetic monopole production in photon fusion process.}\\ 
 & \\ 
16.30 - 17.00 & Vasiliki Mitsou, Oscar Manuel Vives Garcia, Kazuki Sakurai, Roberto Ruiz De Austri\\ 
25+5 min. & {\it Long-lived charged supersymmetric particles and MoEDAL}\\ 
 & \\ 
\end{longtable}

