\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
06.00 - 06.30 & Willibald Plessas\\ 
25+5 min. & {\it Pion-Dressing Effects in Nucleon and Delta Masses and Form Factors}\\ 
 & \\ 
06.30 - 07.00 & Hugo Reinhardt\\ 
25+5 min. & {\it Hamiltonian approach to QCD in Coulomb gauge}\\ 
 & \\ 
07.00 - 07.30 & Mario Mitter\\ 
25+5 min. & {\it Quark, gluon and meson correlators of unquenched QCD}\\ 
 & \\ 
12.00 - 12.30 & Christian Schubert\\ 
25+5 min. & {\it Form factor decompositions of the QCD four-gluon vertex}\\ 
 & \\ 
12.30 - 13.00 & James Edwards\\ 
25+5 min. & {\it Worldline colour fields and non-Abelian quantum field theory}\\ 
 & \\ 
13.30 - 14.00 & Leonid Glozman\\ 
25+5 min. & {\it SU(2N\_F) symmetry of confinement in QCD and its observation at high T}\\ 
 & \\ 
14.00 - 14.30 & Thierry Grandou\\ 
25+5 min. & {\it Effective locality and non-abelian gauge-invariance}\\ 
 & \\ 
14.30 - 15.00 & Ryo Yoshiike\\ 
25+5 min. & {\it Non-linear effect of the fluctuation for the inhomogeneous chiral phase transition}\\ 
 & \\ 
06.30 - 07.00 & Yongmin CHO\\ 
25+5 min. & {\it Weyl symmetric Abelian Decomposition and Monopole}\\ 
 & \\ 
07.00 - 07.30 & Ralf Hofmann\\ 
25+5 min. & {\it SU(2) Yang-Mills thermodynamics: a priori estimate and radiative corrections}\\ 
 & \\ 
08.00 - 08.25 & Andrey Kotov\\ 
20+5 min. & {\it Confinement-deconfinement phase transition in two-color QCD with nonzero baryon density}\\ 
 & \\ 
08.25 - 08.50 & Igor Bogolubsky\\ 
20+5 min. & {\it Gluon correlators and gluon effective mass in lattice QCD}\\ 
 & \\ 
12.00 - 12.30 & David Dudal\\ 
25+5 min. & {\it The linear covariant gauge beyond perturbation theory}\\ 
 & \\ 
12.30 - 13.00 & Christian Lang\\ 
25+5 min. & {\it Hadron Resonances from Lattice QCD}\\ 
 & \\ 
13.30 - 13.55 & Ahmed Bakry\\ 
20+5 min. & {\it Stiff self-interacting strings in high temperature phase of QCD.}\\ 
 & \\ 
\end{longtable}

