\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
12.00 - 12.30 & ATLAS\\ 
25+5 min. & {\it Electron and Photon ID}\\ 
 & \\ 
12.00 - 12.30 & Viktor Riabov\\ 
25+5 min. & {\it Resonance production in Pb-Pb collisions measured with the ALICE experiments at the LHC}\\ 
 & \\ 
12.30 - 13.00 & Cristina Bedda\\ 
25+5 min. & {\it Measurements of D-meson production in p-Pb and Pb-Pb collisions with the ALICE detector at the LHC}\\ 
 & \\ 
12.30 - 13.00 & Samuel Louis Bein\\ 
25+5 min. & {\it CMS Search for new physics in events with jets, b-tagged jets, and large missing transverse momentum in the all-hadronic channel at √s = 13 TeV}\\ 
 & \\ 
13.30 - 14.00 & Maria Vasileiou\\ 
25+5 min. & {\it Transverse momentum spectra and nuclear modification factors of identified charged hadrons in p-Pb and Pb-Pb collisions at √sNN  = 5.02 TeV with ALICE}\\ 
 & \\ 
13.30 - 13.50 & ATLAS\\ 
15+5 min. & {\it Inclusive searches for squarks and gluinos with the ATLAS detector}\\ 
 & \\ 
13.50 - 14.15 & Athina Kourkoumeli-Charalambidi\\ 
20+5 min. & {\it Searches for electroweak production of supersymmetric gauginos and sleptons with the ATLAS detector}\\ 
 & \\ 
14.00 - 14.30 & Agnieszka Łuszczak\\ 
25+5 min. & {\it “Dipole model analysis of highest precision HERA data, including very low $Q^2$”}\\ 
 & \\ 
14.00 - 14.30 & Varvara Batozskaya\\ 
25+5 min. & {\it Measurements of the CP violating phase $phi_s$ at LHCb}\\ 
 & \\ 
14.15 - 14.45 & Sergey Polikarpov\\ 
25+5 min. & {\it Recent CMS B physics results}\\ 
 & \\ 
14.30 - 15.00 & Evgeni Kolomeitsev\\ 
25+5 min. & {\it Fluctuations in non-ideal pion gas with dynamically fixed particle number}\\ 
 & \\ 
12.00 - 12.20 & Alexander Rudenko\\ 
15+5 min. & {\it $f_1 (1285) \to e^+e^-$ decay and direct $f_1$ production in $e^+e^-$ collisions}\\ 
 & \\ 
12.20 - 12.40 & Luca Lista\\ 
15+5 min. & {\it Top-quark results at CMS}\\ 
 & \\ 
13.30 - 14.00 & Dmitry Karlovets\\ 
25+5 min. & {\it Quantum scattering beyond the plane-wave approximation}\\ 
 & \\ 
14.00 - 14.30 & Mirzayusuf Musakhanov\\ 
25+5 min. & {\it Gluons, Heavy and Light Quarks in the QCD Vacuum}\\ 
 & \\ 
14.30 - 15.00 & Masayuki Koga\\ 
25+5 min. & {\it KamLAND-Zen 800 status and future prospects}\\ 
 & \\ 
15.00 - 15.30 & Christian Farnese\\ 
25+5 min. & {\it The ICARUS experiment}\\ 
 & \\ 
13.30 - 14.00 & Jovan Milosevic\\ 
25+5 min. & {\it Sub-leading flow modes in PbPb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV from HYDJET++ model}\\ 
 & \\ 
13.30 - 14.00 & ATLAS\\ 
25+5 min. & {\it ATLAS Jet Reconstruction, Energy Scale Calibration, and Tagging of Lorentz-boosted Objects}\\ 
 & \\ 
13.30 - 14.00 & ATLAS\\ 
25+5 min. & {\it Measurement of cross sections and couplings of the Higgs Boson in bosonic decay channels with the ATLAS detector}\\ 
 & \\ 
13.30 - 14.00 & You Zhou\\ 
25+5 min. & {\it Correlations of anisotropic flow in relativistic heavy-ion collisions at the LHC}\\ 
 & \\ 
14.00 - 14.30 & ATLAS\\ 
25+5 min. & {\it Measurements of the Vector boson production with the ATLAS Detector}\\ 
 & \\ 
14.00 - 14.30 & Francesco Giacosa\\ 
25+5 min. & {\it Non-exponential decay in a quantum field theoretical treatment}\\ 
 & \\ 
14.00 - 14.30 & Riccardo Aliberti\\ 
25+5 min. & {\it Search for K+ to pi+ nu nu at NA62}\\ 
 & \\ 
14.00 - 14.30 & Jovan Milosevic\\ 
25+5 min. & {\it Heavy Ions (CMS)}\\ 
 & \\ 
14.30 - 15.00 & Walter Marcello Bonivento\\ 
25+5 min. & {\it The SHiP experiment at CERN}\\ 
 & \\ 
14.30 - 15.00 & Arantxa Ruiz Martinez\\ 
25+5 min. & {\it The ATLAS Run-2 Trigger Menu for higher luminosities: Design, Performance and Operational Aspects}\\ 
 & \\ 
14.30 - 15.00 & Annapaola De Cosa\\ 
25+5 min. & {\it Dark Matter searches at CMS}\\ 
 & \\ 
14.30 - 15.00 & Letizia Peruzzo\\ 
25+5 min. & {\it Search for heavy neutrinos at the NA48 and NA62 experiments at CERN}\\ 
 & \\ 
15.00 - 15.30 & Roberto Martinez\\ 
25+5 min. & {\it Mass problem in the Standard Model}\\ 
 & \\ 
13.30 - 14.00 & ATLAS\\ 
25+5 min. & {\it Top quark properties and mass measurements with the ATLAS detector}\\ 
 & \\ 
13.30 - 14.00 & Sercan Sen\\ 
25+5 min. & {\it Forward Physics at CMS}\\ 
 & \\ 
14.00 - 14.30 & ATLAS\\ 
25+5 min. & {\it Searches for direct pair production of third generation squarks with the ATLAS detector}\\ 
 & \\ 
14.00 - 14.30 & Norbert Neumeister\\ 
25+5 min. & {\it Standard Model Measurements at CMS}\\ 
 & \\ 
14.30 - 15.00 & ATLAS\\ 
25+5 min. & {\it Search for pair production of new particles in ATLAS}\\ 
 & \\ 
14.30 - 15.00 & Cristiano Alpigiani\\ 
25+5 min. & {\it Ultra long-lived particles searches with MATHUSLA}\\ 
 & \\ 
11.30 - 12.00 & Luis Gonzalez-Mestres\\ 
25+5 min. & {\it The nature and origin of Quantum Mechanics}\\ 
 & \\ 
11.30 - 12.00 & Michael Lublinsky\\ 
25+5 min. & {\it Initial state correlations in the CGC wave function}\\ 
 & \\ 
11.30 - 12.00 & Sergey Mironov\\ 
25+5 min. & {\it Towards topological quantum computer}\\ 
 & \\ 
11.30 - 12.00 & Alexis Kalogeropoulos\\ 
25+5 min. & {\it SUSY (CMS)}\\ 
 & \\ 
12.00 - 12.30 & Mohammed Sanduk\\ 
25+5 min. & {\it The analogy of equation of rotation in complex plane with the Dirac equation, and its foundation}\\ 
 & \\ 
12.00 - 12.30 & Cristi Stoica\\ 
25+5 min. & {\it Wavefunction collapse, conservation laws, and unitary evolution}\\ 
 & \\ 
12.00 - 12.30 & Christophe Royon\\ 
25+5 min. & {\it Forward Physics at the LHC: from the Pomeron structure to the search for anomalous coupling}\\ 
 & \\ 
12.00 - 12.30 & Andre Sopczak\\ 
25+5 min. & {\it SUSY (ATLAS)}\\ 
 & \\ 
12.00 - 12.30 & yogesh kumar\\ 
25+5 min. & {\it Equation of state of quark gluon plasma using a phenomenological model}\\ 
 & \\ 
12.00 - 12.30 & ATLAS\\ 
25+5 min. & {\it Measurements of low energy observables, elastic pp interactions and exclusive production in proton-proton collisions with the ATLAS Detector}\\ 
 & \\ 
12.00 - 12.30 & Bernhard Schwingenheuer\\ 
25+5 min. & {\it Searches for Neutrinoless Double Beta Decays}\\ 
 & \\ 
12.00 - 12.30 & David Mack\\ 
25+5 min. & {\it Searches for a Lepto-phobic “Dark Omega” with the GlueX Detector}\\ 
 & \\ 
12.00 - 12.30 & Sandro Bravar\\ 
25+5 min. & {\it Recent Results from T2K}\\ 
 & \\ 
12.30 - 13.00 & Craig William Evans\\ 
25+5 min. & {\it Towards the first measurement of matter-antimatter gravitational interaction}\\ 
 & \\ 
12.30 - 13.00 & Smbat Grigoryan\\ 
25+5 min. & {\it Using the Tsallis distribution for hadron spectra in pp collisions}\\ 
 & \\ 
12.30 - 13.00 & Lorenzo Bonechi\\ 
25+5 min. & {\it The MURAVES project and parallel activities on cosmic-ray muon absorption radiography}\\ 
 & \\ 
12.30 - 13.00 & Vitaly Bornyakov\\ 
25+5 min. & {\it Lattice QCD at finite baryon density using analytic continuation}\\ 
 & \\ 
12.30 - 13.00 & shihan sajeed\\ 
25+5 min. & {\it Invisible Trojan-horse attack}\\ 
 & \\ 
12.30 - 13.00 & Dragos-Victor Anghel\\ 
25+5 min. & {\it Beyond the phenomenology of the BCS model}\\ 
 & \\ 
13.30 - 14.00 & Yaron Hadad\\ 
25+5 min. & {\it On the relationship between electromagnetic curvature and acceleration of charges}\\ 
 & \\ 
07.00 - 07.30 & ATLAS\\ 
25+5 min. & {\it Recent Tests of the Standard Model with Multi boson final states at the ATLAS Detector}\\ 
 & \\ 
07.00 - 07.30 & Indrani nilima\\ 
25+5 min. & {\it The fate of Quarkonia in an Anisotropic hot QCD medium within a Quasi-Particle Model}\\ 
 & \\ 
07.00 - 07.25 & Swagata Mukherjee\\ 
20+5 min. & {\it Search for Charged Lepton Flavour Violation at CMS}\\ 
 & \\ 
08.00 - 08.30 & Johannes Hoelck\\ 
25+5 min. & {\it Electromagnetic field effects on ϒ meson suppression in PbPb collisions at LHC energies}\\ 
 & \\ 
08.00 - 08.30 & Denise Hellwig\\ 
25+5 min. & {\it Double Chooz double-detector results}\\ 
 & \\ 
08.00 - 08.30 & Elena Luschevskaya\\ 
25+5 min. & {\it Magnetic structure of vector mesons in lattice QCD}\\ 
 & \\ 
08.30 - 09.00 & Wenqing Fan\\ 
25+5 min. & {\it Low Momentum Direct Photon Measurement}\\ 
 & \\ 
08.30 - 09.00 & Aleksandr Korol\\ 
25+5 min. & {\it Measurement of the hadronic cross sections with the CMD-3 and SND detectors at the VEPP-2000 collider}\\ 
 & \\ 
08.30 - 08.50 & Konstantin Astapov\\ 
15+5 min. & {\it TBA}\\ 
 & \\ 
08.50 - 09.15 & Elena Solovieva\\ 
20+5 min. & {\it Excited Charmed Baryons}\\ 
 & \\ 
09.00 - 09.30 & ATLAS\\ 
25+5 min. & {\it Top quark production cross-section measurements}\\ 
 & \\ 
09.00 - 09.30 & Wangmei Zha\\ 
25+5 min. & {\it Calculations of coherent photon-nucleus and photon-photon interactions in hadronic A+A collisions at RHIC and LHC}\\ 
 & \\ 
09.15 - 09.40 & ATLAS\\ 
20+5 min. & {\it Probing QCD with Photons and Jets at the ATLAS Detector}\\ 
 & \\ 
09.30 - 10.00 & Georgios Karathanasis\\ 
25+5 min. & {\it Search for new physics in events with two low momentum opposite-sign leptons and missing transverse energy at √s = 13 TeV}\\ 
 & \\ 
09.30 - 10.00 & Anisa Khatun\\ 
25+5 min. & {\it The measurement of J/$\Psi$ production as function of  multiplicity in pp and p-pb collisions with ALICE}\\ 
 & \\ 
09.40 - 10.05 & ATLAS\\ 
20+5 min. & {\it Tracking and Vertexing with the ATLAS Inner Detector in the LHC Run2 and Beyond}\\ 
 & \\ 
10.00 - 10.30 & Sonja Kabana\\ 
25+5 min. & {\it TBA}\\ 
 & \\ 
12.00 - 12.30 & Cristi Stoica\\ 
25+5 min. & {\it The Standard Model Algebra}\\ 
 & \\ 
12.00 - 12.30 & Sergey Godunov\\ 
25+5 min. & {\it Critical nucleus charge in a superstrong magnetic field}\\ 
 & \\ 
12.30 - 13.00 & Wenqing Fan\\ 
25+5 min. & {\it Recent PHENIX results on high-pT light hadron production}\\ 
 & \\ 
12.30 - 13.00 & Jens Eisert\\ 
25+5 min. & {\it Quantum simulators, boson sampling, and the quest for superior quantum devices}\\ 
 & \\ 
13.30 - 14.00 & Claudio Ciofi degli Atti\\ 
25+5 min. & {\it Nuclear effects in high-energy physics based upon a realistic treatment of short-range nucleon dynamics in nuclei}\\ 
 & \\ 
13.30 - 13.50 & Anthony Lionti\\ 
15+5 min. & {\it Search for magnetic monopoles with the MoEDAL forward trapping detector in 13 TeV proton-proton collisions at the LHC}\\ 
 & \\ 
13.30 - 14.00 & Igor Bulyzhenkov\\ 
25+5 min. & {\it Modified Navier-Stokes equation for conceptual tests of pure field physics}\\ 
 & \\ 
14.00 - 14.30 & Rulin Xiu\\ 
25+5 min. & {\it Inflation Scheme Derived From Universal Wave Function Interpretation of String Theory}\\ 
 & \\ 
05.30 - 06.00 & Raffaele Del Grande\\ 
25+5 min. & {\it Low-energy K$^-$ interaction with light nuclei by the AMADEUS collaboration}\\ 
 & \\ 
06.00 - 06.30 & Konstantin Gusev\\ 
25+5 min. & {\it LEGEND: new opportunity to discover the neutrinoless double beta decay}\\ 
 & \\ 
06.30 - 07.00 & Francesco Terranova\\ 
25+5 min. & {\it The CUORE and CUORE 0 experiments at LNGS}\\ 
 & \\ 
07.00 - 07.30 & Lorenzo Bonechi\\ 
25+5 min. & {\it Overview of LHCf results for Cosmic Ray Studies}\\ 
 & \\ 
07.00 - 07.30 & Sergey Dmitrievsky\\ 
25+5 min. & {\it New results from the OPERA experiment}\\ 
 & \\ 
08.00 - 08.25 & Boris Levchenko\\ 
20+5 min. & {\it New lepton pair production process and possibility of it study at the LHC}\\ 
 & \\ 
08.00 - 08.25 & Takashi Asada\\ 
20+5 min. & {\it Directional dark matter search with nuclear emulsion}\\ 
 & \\ 
08.25 - 08.55 & Andrzej Bozek\\ 
25+5 min. & {\it The Belle II Experiment}\\ 
 & \\ 
08.25 - 08.50 & Pablo G. Ortega\\ 
20+5 min. & {\it Hadronic molecules in a constituent quark model}\\ 
 & \\ 
08.50 - 09.15 & Shabana Nisar\\ 
20+5 min. & {\it Forward-backward asymmetry in top production through z' bosons}\\ 
 & \\ 
\end{longtable}

