\begin{longtable}{p{3cm}p{13cm}}
&\hfill {\bf Convenor INSERT CHAIRMEN }\\ 
11.45 - 12.00 & \\ 
10+5 min. & {\it Opening words}\\ 
 & \\ 
12.00 - 12.30 & Alessandro Romito\\ 
25+5 min. & {\it Ubiquitous non-local entanglement with Majorana bound states}\\ 
 & \\ 
12.30 - 13.00 & Yutaka Shikano\\ 
25+5 min. & {\it Quantum Dynamical Simulation by Quantum Walk}\\ 
 & \\ 
13.30 - 14.00 & Lajos Diosi\\ 
25+5 min. & {\it Pure state post-selection is universal}\\ 
 & \\ 
14.00 - 14.30 & Angelo Bassi\\ 
25+5 min. & {\it Wave function collaspe and gravity}\\ 
 & \\ 
14.30 - 15.00 & Ron Folman\\ 
25+5 min. & {\it Matter waves exposed to the external world: Decoherence, gravity, complementarity and time irreversibility}\\ 
 & \\ 
15.00 - 15.30 & Andrea Alberti\\ 
25+5 min. & {\it Testing the superposition principle with individual trapped atoms}\\ 
 & \\ 
06.00 - 06.30 & OKAMOTO RYO\\ 
25+5 min. & {\it One quantum shutter can close two slits simultaneously}\\ 
 & \\ 
06.30 - 07.00 & Avshalom Elitzur\\ 
25+5 min. & {\it Novel   manifestations	of  quantum oblivion}\\ 
 & \\ 
07.00 - 07.30 & Daniel ROHRLICH\\ 
25+5 min. & {\it Locality and nonlocality in the interaction-free measurement}\\ 
 & \\ 
08.00 - 08.30 & Yakir Aharonov\\ 
25+5 min. & {\it The	fascinating  properties of	weak values}\\ 
 & \\ 
08.30 - 09.00 & Michael Berry\\ 
25+5 min. & {\it Faster than Fourier (pre)visited: vorticulture, noise, fractals...}\\ 
 & \\ 
09.00 - 09.30 & Lev Vaidman\\ 
25+5 min. & {\it The controversy about the past of a quantum particle}\\ 
 & \\ 
12.00 - 12.30 & Sorin Paraoanu\\ 
25+5 min. & {\it Experimental realization of a shortcut to adiabaticity by synthetic Aharonov-Bohm effect in a qutrit}\\ 
 & \\ 
12.30 - 13.00 & Daniel Sheehan\\ 
25+5 min. & {\it Statistical superdegeneracy and quantum foundations}\\ 
 & \\ 
13.30 - 14.00 & Maurice de Gosson\\ 
25+5 min. & {\it Planck's constant as a cosmological variable: transitions from the quantum to the classical}\\ 
 & \\ 
14.00 - 14.30 & David Ellerman\\ 
25+5 min. & {\it Logical Information Theory: New Foundations for Classical and Quantum Information Theory}\\ 
 & \\ 
14.30 - 15.00 & Giuseppe Castagnoli\\ 
25+5 min. & {\it Fundamental mechanism of the quantum computational speedup}\\ 
 & \\ 
06.00 - 06.30 & Shao-Ming Fei\\ 
25+5 min. & {\it Quantum Uncertainty Relations and Related}\\ 
 & \\ 
06.30 - 07.00 & Eli Cohen\\ 
25+5 min. & {\it Quantum Mechanics is Two-Thirds Local Realistic}\\ 
 & \\ 
07.00 - 07.30 & Avishy Carmi\\ 
25+5 min. & {\it Invariance uncertainty determines quantum nonlocality}\\ 
 & \\ 
08.00 - 08.30 & Yuji Hasegawa\\ 
25+5 min. & {\it Counter-intuitive phenomena in quantum mechanics  emerging in matter-wave optical experiments}\\ 
 & \\ 
08.30 - 09.00 & Fabrizio Piacentini\\ 
25+5 min. & {\it Weak Measurements: from Measuring Non-Commuting Observables and Testing Quantum Contextuality to Protective Measurements}\\ 
 & \\ 
09.00 - 09.30 & Avi Pe'er\\ 
25+5 min. & {\it Ultrafast Optical Homodyne - Measuring the Fundamental Variables of Quantum Optics $10^5$ Times Faster}\\ 
 & \\ 
09.30 - 10.00 & Ebrahim Karimi\\ 
25+5 min. & {\it Quantum Cryptography with Structured Photons}\\ 
 & \\ 
\end{longtable}

